---
title: "Résumé<br><br>"
menu: main
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
library(here)
library(lubridate)
library(kableExtra)
library(DT)
library(glue)
library(readxl)
# library(stringi)

# install.packages("remotes")
# remotes::install_github("mitchelloharawild/icons")
# install.packages("fontawesome")
library(fontawesome)



#### all other entries #####
cv_entries <- read_csv("_content/cv_entries_.csv") %>%
  mutate(year_begin = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end)))


blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year_begin = as.character(year_begin),
           year_begin = case_when(
             row_number == 1 ~ year_begin,
             year_begin == lag(year_begin) ~ str_c('<span class="repeated-year">', year_begin, '</span>'),
             year_begin != lag(year_begin) ~ year_begin
           )) %>% 
    mutate(year = if_else(!is.na(lag(year)) & lag(year) == year, 
                          str_c('<span class="repeated-year">', year, '</span>'),
                          year))
}
```



# Summary

:::: {style="display: flex;"}

::: {}
I am currently a Senior Business Administration major with a minor in Finance and Data Analytics at SUNY Geneseo. Following my graduation in May 2022, I have accepted a full-time position at Chubb as an ESIS Partnership Associate located in Melville, NY. Chubb is the world's largest publicly traded property and casualty insurance company. With operations in 54 countries and territories, Chubb provides commercial and personal property and casualty insurance, personal accident and supplemental health insurance, reinsurance and life insurance to a diverse group of clients. As an underwriting company, we assess, assume and manage risk with insight and discipline. We service and pay our claims fairly and promptly. The company is also defined by its extensive product and service offerings, broad distribution capabilities, exceptional financial strength and local operations globally.

My research focuses on student debt and the earnings they make after graduating college. In particular, I am interested in the student debt based on state they attended college in and the earnings they make after they graduate college based on what they studied. I will be creating linear regression models to show the correlation between student debt and earnings after graduation.


Here is my [curriculum vitae](Nicholas Meyer's Resume.pdf) `r fa("fas fa-file-pdf", fill = "red")`.


<div style="text-align: right"> Last updated: `r Sys.Date()` </div>
:::


::: {}
:::

::::

<br>

# Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c( "<span class='cv-entry-title'>", 
                              what, "</span>, ", where,
                              "<br>", 
                       ifelse(is.na(additional_info), "", additional_info) 
                       , "<br>", 
                       ifelse(is.na(additional_info2), "", additional_info2))) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")

```



# Professional Activities
```{r}
cv_entries %>% 
  filter(type == 'prof-act') %>% 
  mutate(what = str_c( "<span class='cv-entry-title'>", 
                              what, "</span>, ", where,
                              "<br>", 
                       ifelse(is.na(additional_info), "", additional_info) 
                       , "<br>", 
                       ifelse(is.na(additional_info2), "", additional_info2))) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")

```

<br>


# Work Experience
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  arrange(desc(date)) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")
```


<br>



# Miscelaneous
## Computing skills
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(icon = case_when(
    str_detect(what, "data analysis") ~ "fa-bar-chart",
    str_detect(what, "research") ~ "fa-flask",
    str_detect(what, "Web") ~ "fa-laptop"
  )) %>% 
  mutate(what = str_c("<i class='fa fa-lg ", icon, "'></i> &nbsp;<span class='cv-entry-title'>", what, "</span> ", additional_info)) %>% 
  select(type, what) %>% 
  mutate(type = "") %>% 
  kbl(padding = 0, col.names = NULL, escape=FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) 
```

<br>


## Skills & volunteering
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(desc(date_end)) %>% 
  select(year, what) %>%
  kbl(padding = 0, col.names = NULL, escape = FALSE)  %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) %>% 
  column_spec(1, width = "15%")
```
